Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
2.4

%--------------------------------------------------------------------------------------------------
\subsection{Timing and Transport Services}

@@

\subsection{Connection and Congestion Control}
We note that \emph{congestion control} is important. Clearly, the historic
belief that real-time applications require an isochronous channel, and
cannot be subjected to congestion control, is not practical on the
Internet. Further, while there is a number of applications that are not
adaptive (and require constant bandwidth), an increasing number are
adaptive, and would better serve users by adapting to the available
bandwidth.

We note that a connection-oriented transport is not a core requirement for
many real-time multimedia applications.  Indeed, flexibility to change the
destination of data within a call could be beneficial for applications that
support mobile users, or for some forms of multiparty session. However, to
support NAT traversal and to help dynamically manage firewall pinholes, it
is often desirable for the transport to be connection oriented. We find
these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service.
Similarly, while not strictly needed by the applications, it is beneficial
if the transport provides a keep-alive service to refresh NAT and firewall
bindings if the application goes silent.

Table \ref{tab:services} summarises the transport services required for
real-time multimedia applications.

>>>>

Table \ref{tab:services} summarises the transport services discussed in this
Section, and required for real-time multimedia applications.
%--------------------------------------------------------------------------------------------------
\subsection{Timing and Transport Services}

@@

\subsection{Connection and Congestion Control}

We note the importance of congestion control. %Clearly,
The historic belief that real-time applications require an isochronous channel,
and should not be subjected to congestion control, is impractical on the
Internet. Further, while some applications are non-adaptive or constant bitrate,
an increasing number are either or both of adaptive and variable bitrate. Such
applications would better serve users by adapting to the available bandwidth.

We note that a connection-oriented transport is a lesser, but useful,
requirement.
% for many real-time multimedia applications.
Indeed, flexibility to
change the destination of data within a call could be beneficial for
applications that support mobile users, or for some forms of multiparty session.
However, to support NAT traversal and to help dynamically manage firewall
pinholes, it is often desirable for the transport to be connection oriented. We
believe these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service. Similarly, while not strictly
needed by the applications, it is beneficial if the transport provides a
keep-alive service to refresh NAT and firewall bindings if the application goes
silent.
